---
title: "MyMap"
author: "Mohammed Teslim"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---
<style>
body {
  font-family: 'Helvetica Neue', Arial, sans-serif;
  margin: 2em; 
  background-color: #002b36; /* Solarized Dark background color */
  color: #839496; /* Solarized Dark base0 color for text */
}
h1, h2 {
  font-weight: bold;
  color: #268bd2; /* Solarized Dark blue color for headers */
  text-align: center;
}
.leaflet-container {
  height: 500px; 
  border: 1px solid #586e75; /* Solarized Dark base01 color for border */
  box-shadow: 3px 3px 5px #073642; /* Solarized Dark base02 color for shadow */
}
.metadata {
  text-align: center; /* Center the author and date */
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```

## My Leaflet Map

```{r map, echo=FALSE, warning=FALSE, message=FALSE, out.extra='id="map"'}
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  setView(lng = -73.9961, lat = 40.7322, zoom = 17) %>% 
  addMarkers(lng = -73.9961, lat = 40.7322, popup = "NYU Center for Data Science") # Add a marker with a popup  # Set the view to London

m
```