---
title: "Exploring Global Development Trends with Gapminder"
author: "Teslim Mohammed"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  ioslides_presentation:
    widescreen: TRUE
    smaller: TRUE
    css: custom.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load necessary libraries
library(gapminder)
library(plotly)
library(dplyr)
```

## Slide 1: Introduction

**Unveiling Global Development Patterns**

-   We're embarking on a journey to explore the **Gapminder dataset**, a treasure trove of information about global development.
-   Our tools: **R** and the interactive power of **Plotly**.
-   Our mission: To visualize and understand the dynamic relationships between:
    -   **Life Expectancy**
    -   **GDP per Capita**
    -   **Population**
    
We will analyze how these vital indicators have changed across the globe and over several decades.

## Slide 2: The Interactive Plot

```{r Slide 2, fig.height=8, fig.width=11}
# Data Preparation
data("gapminder")
gapminder_subset <- gapminder %>%
  filter(year %in% c(1952, 1962, 1972, 1982, 1992, 2002, 2007))

# Create the Plotly bubble chart
p <- gapminder_subset %>%
  plot_ly(
    x = ~gdpPercap,
    y = ~lifeExp,
    size = ~pop,
    color = ~continent,
    frame = ~year, 
    text = ~country,
    hoverinfo = "text",
    type = "scatter",
    mode = "markers",
    marker = list(sizemode = "diameter")
  ) %>%
  layout(
    title = "Life Expectancy vs. GDP per Capita (1952-2007)",
    xaxis = list(title = "GDP per Capita", type = "log"),
    yaxis = list(title = "Life Expectancy"),
    margin = list(t = 100) # Increase top margin to move title up
  ) %>%
  animation_opts(
    frame = 1000,
    transition = 500,
    easing = "linear"
  )
p
```

## Slide 3: Conclusion

**Key Insights**

-   **Positive Trend:** A clear positive correlation exists between GDP per capita and life expectancy. Wealthier nations generally enjoy longer lives.
-   **Continental Divides:** The visualization highlights disparities in development levels across continents.
-   **Global Progress:** The animation demonstrates that most countries have made substantial progress over time, improving both life expectancy and GDP.
-   There are a few outliers that do not follow the trend.

------------------------------------------------------------------------

**Looking Ahead**

This interactive exploration is just the beginning. We can delve deeper by:

-   Adding interactive controls.
-   Integrating more variables from the Gapminder dataset.
-   Performing in-depth statistical analysis.
-   Adding labels to the bubbles

Plotly empowers us to transform data into compelling visual narratives, fostering a deeper understanding of our world.
